\TITLE

### 2021-01-04 response-v3-content.tex

  \REVIEW{DONE} {Needs page number (line number) for ease of
    referencing in the review.}
  {Page numbers and line numbers were
    activated with the review style from the new JDS \LaTeX{}
    template}

  \REVIEW{DONE} {Do not italicize in the text.}
  {All italicized text
    have been removed.  Formulas enclosed in dollar signs are in
    italized text as is default for the JDS document style.}

  \REVIEW{DONE} {AICov needs to be defined in the abstract.}
  {We added ``We present the architecture of an artificial
    intelligence enhanced COVID-19 analysis (in short AICov)''
  in the abstract. We also defined COVID-10 in the abstract.}

\REVIEW{DONE}{Acronyms need to be defined at their first occurrences
  (e.g., AI in the intro). A table of acronyms is included in table 1,
  we added the following acronyms to the paper}
  {All acronyms have been defined at their first usage. In addition
    we have added a section Acronyms in which all acronyms are listed
    to make it easier for the reader to look them up in case they are
    used later on in the paper. All risk factors have been capitalized.
    The duplicated Risk factors were removed.
  }

@@

\REVIEW{TODO}{Figure 2: please present the equations as equations. The
  notations used in the equation need a full check (e.g., h is used as
  both the dimension and vector). I'd like to see a clear distinction
  between inputs/outputs and parameters. I'd suggest that the inputs
  be set up before the equations are presented.}
  { todo}

\REVIEW{DONE}{Regenerate the figures into pdf format (the current
  jpg/png figures blur when zoomed in).}
  {All images have been included as PDF images}

\REVIEW{DONE}{Table 2: consider reformating it; it would not fit the
  page width in print.}
  { Table 2 has been reformatted. It was previously fit in the column
    with resize box. While rotating the headers the font is
    increased. The table still fits in the column as it still uses
    resizebox.Thus it will fit in the print.}

\REVIEW{DONE}{Table 3: tidy the headers.}
  { The headers have been cleaned up and linebreaks were introduced so
    the resizebox of the table presents the table now larger.}

@@

\REVIEW{DONE}{Figure 7-8: can be one figure with two panels; pop
  density 2010 needs to be cleaned.}
    {The figures were combined as subfigures into Figure \ref{fig:error-death-popdensity} (a) and (b)}

\REVIEW{PROGRESS}{Figure 9-14: combine into one figure.}
  {

\todo{the lines are missing in the images showing the NONE line}

First we decided to only display the top 10 results of each prediction
with a factor. Second we have included the combined picture of it for
deaths and cases in the {\bf Figure Combined}. We can include this
figure in the paper if the editor thinks this figure is acceptable. Presently, we have still included these in  subfigure
(a) and (b) in the paper as the scales on the y axis are
clearly distinct. Please let us know what if we need to change this.

@@

%\begin{figure}[!h]
{
        \centering
        \includegraphics[width=.9\textwidth]{images/predict/PlaceTop10_CasesAndDeathNEW2.pdf}

        {\bf Figure Combined} Best predictions for cases over all risk factors.
The two horizontal lines represent the experiment in which no additional Risk factor is used for training. The top one for deaths and the bottom one for cases.}        
        %\label{fig:place-top10-joint}

@@

\bigskip

\REVIEW{DONE}{Page 5, please write the full name for REST
  (representational state transfer) when it first appears.}
  { The term has been defined at first usage, we also checked all
    other abbreviations. }

\REVIEW{DONE}{Page 5, line 3 under Requirement 3, “we are developed an
  abstraction API for data” does not read right.
}
  {The sentence has been corrected to: ``To address this requirement, we are developing an
  abstract API for data, analysis, and metadata parameter
  adjustments.''}

\REVIEW{DONE}{Page 6, line 8, what level is “local level”?
}
  {

  (a) Abstract: the phrase ``local level'' has been removed from the abstract and replaced by ``specific locations''.

  (b) Introduction: The phrase ``at the local level'' has been replaced with ``for the corresponding county'' as a U.S.~county is a well-defined geographical unit of area.

  (c) In Section 4, the sentence containing \linelabel{comment:level}  ``local level'' has been modified as follows:

We use data on community-specific health and behavioral risk factors
aggregated at the county level from the large-scale longitudinal CDC
Behavioral Risk Factor Surveillance System (BRFSS) surveys
\citep{www-cdc-brfss} and demographic and socioeconomic data from the
\citet{www-sensus} for each county, along with the cases and deaths data compiled by
the CDC National Center for Health Statistics (NCHS)
\citep{www-cdc-nchs} and integrate them with other data sources such as the American Hospital Directory \citep{www-ahd}.

@@

}

\REVIEW{PROGRESS}{ Page 7, Table 1, is “CHD” also a percent? If yes
  please modify the description; Percent- blacks and black percent
  both correspond to “Percent of blacks in the population”. Both seem
  to have been used according to Table 3, with difference in the four
  model performance measurements. Do the authors have an explanation
  for this?  }
%
{ (a) The CHD and other values in the table have been updated wherever
  they are given in percent.

@@

\REVIEW{DONE}{Section 5.2, paragraph 2 line 6, no need to capitalize for
  the word “Samples”. Line 5 from the bottom, no need to capitalize
  for the word “Insurance”. Please be careful with your writing.
}
{The capitalization has been corrected. The paper has been reviewed by
  2 native English speakers. In addition 2 grammar checking programs
  were used on the entire paper. One of the reviewers serves also as
  editor in other journals.}

\REVIEW{TODO}{Section 5.2, the “order for cases sorted by minimum model
  order” and “order for deaths sorted by minimum model error”
  paragraphs are redundant, as the same information is already
  displayed in the x-legend for Figures 5 and 6.
}
  { todo}

\REVIEW{TODO}{In Table 3, what is the unit for the error terms? The
  errors in Figures 7 and 8 are percentages. If errors in Table 3 are
  also percentages please clearly mark. Also, the numbers in Figures 7
  and 8 do not align with numbers in row 1 of Table 3. Please check
  your numbers with care.
}
  { todo}

\REVIEW{DONE}{Please adjust the location of your figures so they do not
  look pages apart from their interpretations.
}
  {The locations of the figures have been adjusted, although LaTeX tries to automatically optimize their
  placement. We have used the !h flag to force placement. If this
  placement is still not appropriate, then please let us know. We have also
  removed images in order to facilitate better placement. The
  document is submitted in draft mode which might also influence the
  placement. We have tried the document in final mode with the LaTeX
  style and it seems that the placement is now fixed as we removed images.}

\REVIEW{DONE}{If I am reading it correctly, Figures 9 and 11 are only
  the “zoom in” versions of partial information from Figure
  13. Similarly for the right column. Why waste space on two more
  figures when you could make Figures 13 and 14 bigger and explain the
  findings?
}
  {As we noted in an earlier comment, now we only include the
  Top 10 instead of Top 1, and Top 5, to ensure -- as per the suggestion of the
  reviewers -- that these images are combined. However we still separated
  the deaths from the cases in the figure to ease the readers' ability to view
  more details. However, we can easily replace the image with the ones
  provided earlier if required. This is a minor change and we welcome any further feedback on this from the reviewers.}

### 2021-01-04 vonLaszewski-covid.tex
Updates from Overleaf

\affil[1]{Digital Science Center, Indiana University, Bloomington Indiana, USA}
\affil[2]{Public Health Dynamics Lab, and Department of Biostatistics,
  University of Pittsburgh, Pittsburgh, Pennsylvania, USA}
\affil[3]{Health Analytics Network, Pennsylvania, USA}

@@

For precise and contextually relevant modeling of COVID-19 dynamics
for a given population or community, we use data integration to
combine community-specific health and behavioral risk factors,
demographic and socioeconomic variables that are available at the
local along with the cases and deaths data for COVID-19 while
leveraging the recently developed and increasingly popular deep
learning strategies to forecast COVID-19 dynamics using our
model. Towards this, we develop a parallel computing platform called
AICov standing for AI-driven Platform for COVID-19 to implement the
different components of our framework and obtain the needed resources
through multi-cloud interfaces in a robust manner.

@@

While the U.S. has seen an overall case fatality rate of 5.14\%, some
U.S. locations have experienced a disproportionate number of deaths
compared to others. This disparity of deaths among different
communities could be attributed to a diversity of local risk factors
and socioeconomic determinants of health that now constitute a very
active area of investigation. Researchers are studying the effects of
different community-specific socioeconomic variables, underlying
health conditions and comorbidities, infrastructure, and systemic
responses.  Given the complexity of such underlying conditions that
can determine individual disease outcomes, where and under what
conditions people get infected by the virus, and then recover or die
take place not in isolation but rather in an interplay of diverse
factors that are characteristic to a local community, which need to be
synthesized. In other words, a basic requirement for effective
modeling of COVID-19 dynamics is that the information regarding a
particular community’s vulnerabilities and strengths pertaining to the
disease must be as comprehensive and integrative as possible.  The
regular reporting of accurate Coronavirus outbreaks data from local
health departments has been understandably difficult, especially in
the areas that are hardest hit.
%
\linelabel{comment:level} We use data on community-specific health and
behavioral risk factors aggregated at the county level from the
large-scale longitudinal CDC Behavioral Risk Factor Surveillance
System (BRFSS) surveys \citep{www-cdc-brfss} and demographic and
socioeconomic data from the U.S. Census Bureau \cite{www-sensus},
i.e., both at the county and census tract, along with the cases and
deaths data compiled by the CDC National Center for Health Statistics
(NCHS) \citep{www-cdc-nchs} and integrate them with other data
sources. These other data sources include

\todo{Pyne}.

@@

We conducted one additional analysis and plotted the top 10 best
cummulative prediction model errors for each risk factor in
Figure \label{fig:place-top10} for cases and deaths.  The horizontal
black line shows the first occurance of no risk factor being used.

Notably, we identified that a jump occurs when we sort the top 10
model predictions at around 330 models from a total of 3400
automatically generated models. This also underscores the need to run
our deep learning model multiple times to obtain best parameter
candidates.  Furthermore, we see that the cummulative error for cases
is about half the size as for death. This is caused by cases having a
larger number of sample.

@@

%    \begin{minipage}{.45\textwidth}
%        \centering
%        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop5_Cases.pdf}
%        \vspace{-1cm}
%        \caption{Top 5 predictions from all cases over all risk factors.}
%        \label{fig:place-top5-cases}
%    \end{minipage}
%    \ \
%    \begin{minipage}{.45\textwidth}
%        \centering
%        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop5_Death.pdf}
%        \vspace{-1cm}
%        \caption{Top 5 predictions from all deaths  over all risk factors.}
%        \label{fig:place-top5-death}
%    \end{minipage}
    \begin{subfigure}{.95\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_Death.pdf}
        \caption{Cumulatice error for deaths.}
        \label{fig:place-top10-death}
    \end{subfigure}
    \begin{subfigure}{.95\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_Cases.pdf}
        \caption{Cummulative error for cases}
        \label{fig:place-top10-cases}
    \end{subfigure}

    \caption{Top 10 predictions from all differnt risk factors sorted by cummulative error for deaths (\ref{fig:place-top10-death}) and cases (\ref{fig:place-top10-cases}). The horizontal line in each figure represents the model cummulative error with no risk factor as input for deaths and cases respectively.}
    \label{fig:place-top10}

>>>>

\affil[1]{Digital Science Center, Indiana University, Bloomington Indiana, USA}
\affil[2]{Public Health Dynamics Laboratory, and Department of Biostatistics,
  University of Pittsburgh, Pittsburgh, Pennsylvania, USA}
\affil[3]{Health Analytics Network, Pennsylvania, USA}

@@

For precise and contextually relevant modeling of COVID-19 dynamics
for a given population or community, we use data integration to
combine community-specific health and behavioral risk factors,
demographic and socioeconomic variables that are available for the corresponding county along with the cases and deaths data for COVID-19 while
leveraging the recently developed and increasingly popular deep
learning strategies to forecast COVID-19 dynamics using our
model. Towards this, we develop a parallel computing platform called
AICov standing for AI-driven Platform for COVID-19 to implement the
different components of our framework and obtain the needed resources
through multi-cloud interfaces in a robust manner.

@@

While the U.S. has seen an overall case fatality rate of 5.14\%, some
U.S. locations have experienced a disproportionate number of deaths
compared to others. This disparity of deaths among different
communities could be attributed to a diversity of local risk factors
and socioeconomic determinants of health that now constitute a very
active area of investigation. Researchers are studying the effects of
different community-specific socioeconomic variables, underlying
health conditions and comorbidities, infrastructure, and systemic
responses.  Given the complexity of such underlying conditions that
can determine individual disease outcomes, where and under what
conditions people get infected by the virus, and then recover or die
take place not in isolation but rather in an interplay of diverse
factors that are characteristic to a local community, which need to be
synthesized. In other words, a basic requirement for effective
modeling of COVID-19 dynamics is that the information regarding a
particular community’s vulnerabilities and strengths pertaining to the
disease must be as comprehensive and integrative as possible.  The
regular reporting of accurate Coronavirus outbreaks data from local
health departments has been understandably difficult, especially in
the areas that are hardest hit.
%
\linelabel{comment:level} We use data on community-specific health and
behavioral risk factors aggregated at the county level from the
large-scale longitudinal CDC Behavioral Risk Factor Surveillance
System (BRFSS) surveys \citep{www-cdc-brfss} and demographic and
socioeconomic data from the U.S. Census Bureau \cite{www-sensus} for each county, along with the cases and
deaths data compiled by the CDC National Center for Health Statistics
(NCHS) \citep{www-cdc-nchs} and integrate them with other data
sources such as the American Hospital Directory \citep{www-ahd}.

@@

We conducted one additional analysis and plotted the top 10 best
cumulative prediction model errors for each risk factor in
Figure \label{fig:place-top10} for cases and deaths.  The horizontal
black line shows the first occurrence of no risk factor being used.

Notably, we identified that a jump occurs when we sort the top 10
model predictions at around 330 models from a total of 3400
automatically generated models. This also underscores the need to run
our deep learning model multiple times to obtain best parameter
candidates.  Furthermore, we see that the cumulative error for cases
is about half the size as for death. This is caused by cases having a
larger number of sample.

@@

%    \begin{minipage}{.45\textwidth}
%        \centering
%        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop5_Cases.pdf}
%        \vspace{-1cm}
%        \caption{Top 5 predictions from all cases over all risk factors.}
%        \label{fig:place-top5-cases}
%    \end{minipage}
%    \ \
%    \begin{minipage}{.45\textwidth}
%        \centering
%        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop5_Death.pdf}
%        \vspace{-1cm}
%        \caption{Top 5 predictions from all deaths  over all risk factors.}
%        \label{fig:place-top5-death}
%    \end{minipage}
    \begin{subfigure}{.95\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_Death.pdf}
        \caption{Cumulative error for deaths.}
        \label{fig:place-top10-death}
    \end{subfigure}
    \begin{subfigure}{.95\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{images/predict/PlaceTop10_Cases.pdf}
        \caption{Cumulative error for cases}
        \label{fig:place-top10-cases}
    \end{subfigure}

    \caption{Top 10 predictions from all different risk factors sorted by cumulative error for deaths (\ref{fig:place-top10-death}) and cases (\ref{fig:place-top10-cases}). The horizontal line in each figure represents the model cumulative error with no risk factor as input for deaths and cases respectively.}
    \label{fig:place-top10}
